\chapter{Scenarios identifying}
In this section we are going to analyze some of the possible scenarios derived from the use of PowerEnJoy.

\section{Scenario 1}
Nick wants to go to his friend's wedding anniversary. He has come to know about the PowerEnJoy car-sharing service through some advertisements. He visits the website for the first time. He realizes that he needs to become a registered user in order to reserve an available car. He decides to register in the website and becomes a registered user after filling the mandatory details (driving license, codice fiscale, etc.) and completing the payment successfully. He receives his credentials (user ID, password) for further sign in.

Without knowing about the benefits and constraints of the PowerEnJoy, he just reserves an available car and travels to his destination and ends his ride after parking the reserved car in a nearby area to the place of his destination. Fortunately, it turns out to be a safe parking area and he has left the car with 60\% of battery. He is notified of the final price mentioning that he has received 20\% discount. Nick leaves the reserved car happily.

\section{Scenario 2}
After getting the knowledge of the benefits and constraints from the website of PowerEnJoy, Nick wants to reserve a car to attend a meeting in his office. This time, two of his colleagues are there with him and he reserves a nearby available car.

He takes a ride with the two colleagues, reaches the destination with more than 50\% of battery charge remaining, parks in a safe area and gets an overall discount for 30\% by the system (10\% for riding with at least two extra passengers and 20\% for not draining the battery more than 50\%). Nick leaves the reserved car happily.

\section{Scenario 3}
Right after the scenario 2, Nick receives a telephone call saying that his wife is in maternity pain and he needs to take her to the hospital immediately. Meanwhile, the parked car (after Nick's ride) is the only nearest car for him. He decides to open the car and then reserve it.

Meanwhile, this parked car has been reserved by someone else and Nick is not even able to open the door of the parked car (since he was not able to reserve that car and hence the communication with that car is not possible). Finally, he searches for the other available cars and then takes a ride.

\section{Scenario 4}
Frank is a registered user to the PowerEnJoy service. He wants to make a ride to his university which is very far from his home. Frank reserves an available car with PowerEnJoy and rides to his college where he parks the reserved car in a safe area but has consumed more than 80\% of the battery.

So, he is charged 30\% more on his ride and Frank is notified about the final charge.

\section{Scenario 5}
Frank needs to take his girlfriend to a pub on a Saturday night. He decides to use the PowerEnJoy service. As he is a registered user, he reserves an available car. But his girlfriend arrives late. Also, so it has been more than an hour since he made the reservation and did not pick the reserved car.

Hence he is charged or penalized with \EUR{1} and the reservation he made has been expired. So, Frank needs to start the process again.

\section{Scenario 6}
James is a registered user to the PowerEnJoy service. He has gone to Lugano (Switzerland) for a business visit. He has found PowerEnJoy to be cheaper than the train and decides to reserve an available car from Lugano (Swiss) to Milan (Italy), which is a cross country travel.

When he searches for the available cars to make a reservation, he is not able to spot any cars, in his geographical region as PowerEnJoy restricts cross country travel which are against its terms and conditions.

\section{Scenario 7}
James wants to save money, hence he activates the money saving option. As a registered user, he selects his destination and picks an available car. He is notified from the system about the station where he needs to park the reserved car in order to avail of the discount.

But, in a hurry, James leaves the reserved car in a safe area and ends the ride. Thus, he did not receive any discount in his final charge after the end of his ride.

\section{Scenario 8}
Mr.~Potter is a guest to the PowerEnJoy service and he wants to register himself to make a ride when he needs. He uploads all the mandatory documents in the web page and registers himself after completing the payment successfully. He reserves an available car and travels more than the amount which he has paid while registering. He parks the reserved car in a safe area and ends his ride.

Mr.~Potter is notified by the system that he must pay the balance by three days from the end of the ride otherwise his documents (driving license, codice fiscale, etc.) will be sent or notified to the local police, stating the issue and serious action will be taken against him as per the law. Also, he loses the privilege of being a prestigious member of PowerEnJoy and its services.